Proposal: Loose Grammar Inference for Lossy Compression

### 2012-10-18 proposal.tex
~Finishing intro

>>>>

The scope of our focus will be like that of \Sequitur: we will consider the
composite application of both grammar transformation and grammar compression to
an input.

There seems to be little existing work done in the intersection of grammar
compression and lossy compression.  Thus, we will compare our work to existing
techniques both in lossless hierarchical compression and lossy non-hierarchical
compression.  Moreover, we will not concern ourselves with fitting our lossy
grammar compression into overarching information-theoretic developments.
